Limb-darkening and exoplanets II: Choosing the Best Law for Optimal Retrieval of Transit Parameters

### 2016-01-20 first_response_to_referee.txt

 We thank the referee for his/her careful reading of the manuscript. 
 You will find below our detailed response to the referee's comments 
 as indented text after each of his/her comments.

 Besides the changes made in response to the referee's comments we have:

     - Corrected minor typos on the manuscript.

     - Changed the title of the manuscript to reflect the additional study 
       proposed by the referee on the precision of the retrieved transit 
       parameters, which implies we now not only help to decide the law 
       that provide minimum bias, but also the one that is optimal in a mean squared error sense.

     - Added extra text on the Abstract, Introduction and Section 3 to reflect 
       these changes in the study. This includes a change of the name of Section 3, and an additional sub-section explaining the procedures used to study the bias/variance trade-off.

     - Modified the Acknowledgments.

@@

########################################################################################
>> My main suggestion is that the paper would benefit from a more quantitative 
>> description of the trade-off between precision and accuracy. This work indicates 
>> that fitting for two limb darkening coefficients with a judiciously chosen model 
>> can significantly reduce bias. In practice, however, many light curves are not 
>> sufficiently precise to tightly constrain more than one limb darkening parameter. 
>> Adding an additional degree of freedom with a second limb darkening coefficient 
>> may cause the uncertainty on other important parameters, particularly the transit 
>> depth, to blow up. The resulting loss in accuracy may not be worth the improvement 
>> in precision due to choosing a two-parameter model over fitting for  a linear limb 
>> darkening coefficient.
>>
>> One way to address this question is to give guidelines about how precise a 
>> light curve must be to merit adding a second limb darkening parameter to the 
>> model. This could be discussed for a few select examples (e.g., a hot Jupiter 
>> transiting a Sun-like star).  I leave it up to the authors whether/how to address 
>> this point.

We thank the referee for this very insightful suggestion. We have made a whole suite of 
simulations which exactly answers this question, and provide code so future researchers 
can decide which is the best law both in terms of bias and precision for their specific 
application; in this way, researchers can decide the optimal limb-darkening law for the 
lightcurve at hand. These simulations are shown and discussed both on Section 3.4 and 
Section 4.

### 2016-01-20 which_law_2_use.tex
final edit before resub

\begin{abstract}
Very precise measurements of exoplanet transit lightcurves both from ground and space based observatories make it now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler (e.g., the linear law) or 
better descriptions of model intensity profiles. In this work, we show that laws such as the 
logarithmic, square-root and three-parameter law do a better job that the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
bias and precision, for a wide range of situations. We therefore recommend to study which law to 
use on a case-by-case basis. We provide code to guide the decision of when to use each of these laws and select the optimal one in a 
mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

In the past decade, the study of transiting exoplanets has evolved from discovery to very precise characterization of these systems, 
thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of  obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
measurements \citep{dorn2015} and of their atmospheric fractions from radius measurements alone \citep{WL2015}. In addition, precise transit lightcurves enable the determination of
derived parameters of the systems that even allow for the estimation of stellar parameters directly from transit lightcurves through techniques such as asterodensity
profiling \citep{sm2003,kipping2014AP}, and the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
All these studies and techniques rely on the retrieval of {\em precise and accurate} transit parameters from transit lightcurves.

@@

Given the above, unless the data quality is really poor (and one is willing to trade bias for variance), there is actually no good reason to fix the limb-darkening coefficients 
in the transit fitting process (assuming computational resources are not an issue). However, although fitting the 
limb-darkening coefficients seems to be a good solution to the accuracy problem, there remains the issue of the low flexibility of the quadratic limb-darkening 
law which can cause important biases on the retrieved transit parameters as shown in EJ15. These biases can be as large as $\sim 1\%$ for the planet-to-star 
radius ratio $R_p/R_*$, $\sim 2\%$ for the scaled semi-major axis, $a/R_*$, and $2\%$ for the inclination, where $R_p$ is the planetary radius, $R_*$ 
the stellar radius and $a$ the semi-major axis. The importance for missions like {\em Kepler} and for future missions like the Transiting Exoplanet Survey 
Satellite \cite[TESS,][]{ricker2014} is evident when looking at the most recent results from the {\em Kepler} mission: if we focus on the planet-to-star radius ratio measurements 
alone, which according to EJ15 have an accuracy bias on the order of $\sim 0.2\%$, a query to the Nasa Exoplanet Archive\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; query done on 29/09/2015.} shows that out of 3063 planetary candidates, 933 ($26\%$) have precisions better than 
$0.2\%$, and out of 1001 {\em Kepler} confirmed exoplanets, 463 (46\%) do too. This means that at least\footnote{It is important to note that this is an 
underestimate of the number of planet candidates with estimation errors, due to the fact that the Kepler pipeline makes use of fixed limb-darkening 
coefficients using the quadratic law \citep{rowe2015}, which as explained here and estimated in EJ15, gives rise to more severe biases than the one used for this 
estimation} $26\%$ of the planet candidates (from which, e.g., population studies, which rely on averaging out \textit{random} and not \textit{systematic} 
uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets (from which, e.g., characterization studies are 
based on) have significant systematic errors.

@@

Despite the attractive nature of the above mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
lightcurves was problematic until recently for two reasons. First, there was no publicly available code capable of efficiently generating fast and accurate 
transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
algorithm that does exactly this called \texttt{batman}, enabling the generation of transit lightcurves very efficiently with any arbitrary limb-darkening law. 
The second problem was that it was not clear how to sample limb-darkening coefficients in an informative (i.e., sampling all the physically possible parameter 
space) and efficient way for all of these laws. Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing 
physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted. \cite{kipping2013}, using the 
same principles, derived an algorithmic way of doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus 
no constrains for this law could be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
\cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one has to derive an efficient  informative sampling scheme for it.

@@

\section{Optimal selection of limb-darkening laws}
Having dealt with the sampling of limb-darkening coefficients from the 
logarithmic and exponential laws, we are now ready to turn to the study of the performance 
of the most popular limb-darkening laws (i.e., the linear, quadratic, logarithmic, square-root and 
three-parameter laws) both in terms of bias and precision in the 
retrieval of transit parameters. In particular, we focus on the performance of the retrieval of the planet-to-star 
radius ratio, $p=R_p/R_*$, the scaled semi-major axis, $a_R = a/R_*$ and the inclination, $i$, from transit lightcurves. 
In this section, we first study the biases introduced by using different limb-darkening laws, and then we study the 
bias-variance trade-off between different laws.

\subsection{Biases in the retrieval of transit parameters}
In order to study the biases introduced by different parametrizations of the limb-darkening effect, we perform a similar study 
as the one done in EJ15, but now (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using the 
linear law, three different two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter 
law and (3) using a smaller number of steps in the planet-to-star radius ratio, in order to illustrate the evolution of the biases 
with this parameter in a cleaner way: we choose to study small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones 
($p=0.13$).

@@

\subsubsection{The case of central transits}
\begin{figure*}
\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. Note that the scale shown for the linear law is different 
than the one used in the figures for the other laws. The size of the points is proportional to the the input values of $p$.}
\label{central_sims}
\end{figure*}

@@

\subsubsection{The case of non-central transits}
\begin{figure*}
\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.3/simulation_b_03_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for low impact 
parameter transits ($b=0.3$). Note that the scale shown for the linear law is different than the one used in the figures for the other laws. The 
size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
\label{small_b_sims}
\end{figure*}

@@

\subsection{The bias-variance trade-off}
\begin{figure}
\includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{\theta}$ of 
the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
want a low bias, high precision estimator.}
\label{bias-variance-plot}
\end{figure}

From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimize the 
biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
actually provide enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
the cost. Fitting a complex law to a noisy light curve will definitely lower the precision of the retrieved transit parameters due to the high flexibility of the 
model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
ammounts of bias and variance, and thus choosing among them is, at first, not trivial. This is when the mean-squared error metric comes in handy. The mean-squared 
error (MSE) of an estimator $\hat{\theta}$ of the parameter $\theta$ is defined as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2].
\end{eqnarray*}
From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value. This provides a metric among a given suite of estimators for a given parameter: the one that gives the minimum mean-squared error 
provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2], \\
&=& (\mathbb{E}[\hat{\theta}]-\theta)^2 + \textnormal{Var}[\hat{\theta}],\\
&=& \textnormal{Bias}^2 + \textnormal{Variance}.
\end{eqnarray*}
This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We have thus already
calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
used to retrieve the transit parameters.

@@

It is evident from our results how the MSE evolves from being variance-dominated for low-noise lightcurves (rightmost part of the plot) to bias-dominated for high-noise 
lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
$\approx100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with easse. For example, in our simulation, for $N=100$ in-transit points, 
the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
At this last noise level, we see that the square-root law crosses the line of the logarithmic law, and this latter law attains the lowest MSE until $\approx 200$ ppm, where the 
quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\approx 200$ ppm until lightcurves with precisions of $\approx25$ ppm, a noise level at 
which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes the  points at which the transition among different limb-darkening 
laws occur due to the fact that the bias floor is attained faster as a consequence of the increased number of points. For example, the transition between the quadratic and three-parameter 
laws occurs for lower precision lightcurves for the case of $1000$ in-transit points (at $\approx 75$ ppm).

From our case study, we propose that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation:  for a given observational setup in terms of cadence and noise, simply calculate the MSE obtained 
by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one favourites' law, obtain a set of 
transit parameters, and use those as inputs in order to calculate the MSE of different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives 
the lowest MSE. We provide code at Github with which this process can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and 
number of in-transit points.

@@

The question of when to use each of those laws is an important one. In particular, we have explored the relation between the real, underlying 
transit parameters, the stellar host properties and the bias/variance on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
law, but rather provided guidelines based on our simulations. This is a choice made on purpose, as the selection of which law to use has to be done in a 
case-by-case basis, a task for which we provide code with which one can obtain the results of the same simulations performed on our work for specific 
cases \footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
{\em Kepler} bandpass to study the relation between the biases/variances on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
rise to  different functional relations because they give rise to different model intensity profiles. Limb-darkening coefficients have to be calculated for each  particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.

>>>>

\begin{abstract}
Very precise measurements of exoplanet transit lightcurves both from ground and space based observatories make it now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
errors which directly impact the physical properties of the system derived from such lightcurves such as the planetary radius. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler or 
better descriptions of model intensity profiles. In this work, we show that laws such as the 
logarithmic, square-root and three-parameter law do a better job that the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
bias and precision, for a wide range of situations. We therefore recommend to study which law to 
use on a case-by-case basis. We provide code to guide the decision of when to use each of these laws and select the optimal one in a 
mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

In the past decade, the study of transiting exoplanets has evolved from discovery to very precise characterization of these systems, 
thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of  obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass and radius
measurements \citep{dorn2015} and of their atmospheric fractions from radius measurements alone \citep{WL2015}. In addition, precise transit lightcurves enable the determination of
derived parameters of the systems that even allow for the estimation of stellar parameters directly from transit lightcurves through techniques such as asterodensity
profiling \citep{sm2003,kipping2014AP}, and the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
All these studies and techniques rely on the retrieval of {\em precise and accurate} transit parameters from transit lightcurves.

@@

Given the above, unless the data quality is really poor (and one is willing to trade bias for variance), there is actually no good reason to fix the limb-darkening coefficients 
in the transit fitting process (assuming computational resources are not an issue). However, although fitting the 
limb-darkening coefficients seems to be a good solution to the accuracy problem, there remains the issue of the low flexibility of the quadratic limb-darkening 
law which can cause important biases on the retrieved transit parameters as shown in EJ15. These biases can be as large as $\sim 1\%$ for the planet-to-star 
radius ratio $R_p/R_*$, $\sim 2\%$ for the scaled semi-major axis, $a/R_*$, and $2\%$ for the inclination, where $R_p$ is the planetary radius, $R_*$ 
the stellar radius and $a$ the semi-major axis. The importance for missions like {\em Kepler} and for future missions like the Transiting Exoplanet Survey 
Satellite \cite[TESS,][]{ricker2014} is evident when looking at the most recent results from the {\em Kepler} mission: if we focus on the planet-to-star radius ratio measurements 
alone, which according to EJ15 have an accuracy bias on the order of $\sim 0.2\%$, a query to the Nasa Exoplanet Archive\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; query done on 29/09/2015.} shows that out of 3063 planetary candidates, 933 ($26\%$) have precisions better than 
$0.2\%$, and out of 1001 {\em Kepler} confirmed exoplanets, 463 (46\%) do too. This means that at least\footnote{It is important to note that this is an 
underestimate of the number of planet candidates with estimation errors, due to the fact that the Kepler pipeline makes use of fixed limb-darkening 
coefficients using the quadratic law \citep{rowe2015}, which as explained here and estimated in EJ15, gives rise to more severe biases than the one used for this 
estimation} $26\%$ of the planet candidates (from which, e.g., population studies, which rely on averaging out \textit{random} and not \textit{systematic} 
uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets have significant systematic errors.

@@

Despite the attractive nature of the above mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
lightcurves was problematic until recently for two reasons. First, there was no publicly available code capable of efficiently generating fast and accurate 
transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
algorithm that does exactly this called \texttt{batman}, enabling the generation of transit lightcurves very efficiently with any arbitrary limb-darkening law. 
The second problem was that it was not clear how to sample limb-darkening coefficients in an informative (i.e., sampling all the physically possible parameter 
space) and efficient way for all of these laws. Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing 
physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted. \cite{kipping2013}, using the 
same principles, derived an algorithmic way of doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus 
no constrains for this law could be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
\cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one needs to derive an efficient  informative sampling scheme for it.

@@

\section{Optimal selection of limb-darkening laws}

Having dealt with the sampling of limb-darkening coefficients from the 
logarithmic and exponential laws, we are now ready to turn to the study of the performance 
of the most popular limb-darkening laws (i.e., the linear, quadratic, logarithmic, square-root and 
three-parameter laws) both in terms of bias and precision in the 
retrieval of transit parameters. In particular, we focus on the performance of the retrieval of the planet-to-star 
radius ratio, $p=R_p/R_*$, the scaled semi-major axis, $a_R = a/R_*$ and the inclination, $i$, from transit lightcurves. 
In this section, we first study the biases introduced by using different limb-darkening laws, and then we study the 
bias-variance trade-off between different laws.

\subsection{Biases in the retrieval of transit parameters}

In order to study the biases introduced by different parametrizations of the limb-darkening effect, we perform a similar study 
as the one done in EJ15, but now (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using the 
linear law, three different two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter 
law and (3) using a smaller number of steps in the planet-to-star radius ratio, in order to illustrate the evolution of the biases 
with this parameter in a cleaner way: we choose to study small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones 
($p=0.13$).

@@

\subsubsection{The case of central transits}

\begin{figure*}
\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. Note that the scale shown for the linear law is different 
than the one used in the figures for the other laws. The size of the points is proportional to the the input values of $p$.}
\label{central_sims}
\end{figure*}

@@

\subsubsection{The case of non-central transits}

\begin{figure*}
\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.3/simulation_b_03_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for low impact 
parameter transits ($b=0.3$). Note that the scale shown for the linear law is different than the one used in the figures for the other laws. The 
size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
\label{small_b_sims}
\end{figure*}

@@

\subsection{The bias-variance trade-off}

\begin{figure}
\includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{\theta}$ of 
the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
want a low bias, high precision estimator.}
\label{bias-variance-plot}
\end{figure}

From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimize the 
biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
actually provide enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
the cost. Fitting a complex law to a noisy light curve will definitely lower the precision of the retrieved transit parameters due to the high flexibility of the 
model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
square-root defines the inverse precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
ammounts of bias and variance, and thus choosing among them is, at first, not trivial. This is when the mean-squared error metric comes in handy. The mean-squared 
error (MSE) of an estimator $\hat{\theta}$ of the parameter $\theta$ is defined as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2].
\end{eqnarray*}
From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value. This provides a metric among a given suite of estimators for a given parameter: the one that gives the minimum mean-squared error 
provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2], \\
&=& (\mathbb{E}[\hat{\theta}]-\theta)^2 + \textnormal{Var}[\hat{\theta}],\\
&=& \textnormal{Bias}^2 + \textnormal{Variance}.
\end{eqnarray*}
This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We have thus already
calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
used to retrieve the transit parameters.

@@

It is evident from our results how the MSE evolves from being variance-dominated for low-noise lightcurves (rightmost part of the plot) to bias-dominated for high-noise 
lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
$\approx100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with ease. For example, in our simulation, for $N=100$ in-transit points, 
the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
At this last noise level, we see that the square-root law crosses the line of the logarithmic law, and this latter law attains the lowest MSE until $\approx 200$ ppm, where the 
quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\approx 200$ ppm until lightcurves with precisions of $\approx25$ ppm, a noise level at 
which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes the  points at which the transition among different limb-darkening 
laws occur due to the fact that the bias floor is attained faster as a consequence of the increased number of points. For example, the transition between the quadratic and three-parameter 
laws occurs for lower precision lightcurves for the case of $1000$ in-transit points (at $\approx 75$ ppm).

From our case study, we propose that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation:  for a given observational setup in terms of cadence and noise, simply calculate the MSE obtained 
by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one's favourite law, obtain a set of 
transit parameters, and use those as input in order to calculate the MSE of different limb-darkening laws and then retrieve the final transit parameters using the law that gives 
the lowest MSE. We provide code at Github with which this process can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and 
number of in-transit points.

@@

The question of when to use each of those laws is an important one. In particular, we have explored the relation between the ``real", underlying 
transit parameters, the stellar host properties and the bias/variance on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
law, but rather provided guidelines based on our simulations. This is a choice made on purpose, as the selection of which law to use has to be done in a 
case-by-case basis, a task for which we provide code with which one can obtain the results of the same simulations performed on our work for specific 
cases \footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
{\em Kepler} bandpass to study the relation between the biases/variances on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
rise to  different functional relations because they give rise to different model intensity profiles. Limb-darkening coefficients have to be calculated for each  particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.
